---
title: "ioLabs-mosaic2"
author: ""
date: "7/2/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mosaic)
library(devtools)
```

Source files for OpenIntro Statistics labs using mosaic modeling approach and ggformula.

Builds upon the prior work of 
[https://github.com/beanumber/oiLabs-mosaic](https://github.com/beanumber/oiLabs-mosaic)
(last updated November 29, 2016).

The mosaic package is designed to facilitate the use of R in statistics and
calculus instruction by providing a number of functions that (a) make many
common tasks fit into a common template, and (b) simplify some tasks that would
otherwise be too complicated for beginners.  See
[https://github.com/ProjectMOSAIC/mosaic]
(https://github.com/ProjectMOSAIC/mosaic)
for more information.

The oilabs package contains the data sets, custom functions, documentation, 
and templates for the OpenIntro Labs 
(see 
[http://openintrostat.github.io/oilabs](http://openintrostat.github.io/oilabs)
and 
[https://github.com/OpenIntroStat/oilabs](https://github.com/OpenIntroStat/oilabs)).

## Required R packages

To use these materials, a number of pakcages must be installed.  

```{r, eval = FALSE}
# install.packages("devtools")
libary(devtools)
install.packages("mosaic")
install_github("OpenIntroOrg/openintro-r-package", subdir = "openintro", build_vignettes = TRUE)
devtools::install_github("openIntroStat/oilabs", build_vignettes = TRUE)
```

## Building documents

`make.R` contains the commands required to build the documents.


